\begin{abstract}[english][Abstract]
\keywords[Keywords]{Password Manager, Biometric Authentication, Encryption}

Thousands of services are offered on the web, and the vast majority of them use some form of authentication, usually through username and password. However, the use of passwords can make authentication fragile when it is very simple, with reduced security. On the other hand, when they are complex and very large they are difficult to memorize and users often keep notes of these in unsafe places, making the process fragile. In this way, password management systems can be a solution to avoid the use of weak and repeated passwords in different services without the need to be memorized or annotated by the user. In one hand, one need to securely store passwords using encryption techniques so that information security is present at all times, no matter where they are stored. There are several techniques and algorithms for data encryption, some are extremely secure and others not so much. On the other hand, it is necessary to use efficient methods of authentication in these systems, because once someone can access them, all saved passwords can be seen. Thus, a good alternative is biometric authentication using features such as faces and voice, which can provide an extra layer of security, while improving the convenience in its use. The technology present in the current devices allows the development of systems that are capable of processing biometric features with few computational resources, and have the necessary sensors for the process of collecting samples of them, through cameras, microphones and digital readers. This work presents the design of a secure password storage and generation system using encryption and biometric authentication.
\end{abstract}