\begin{abstract}[english][Abstract]
\keywords[Keywords]{Password Manager, Biometric Authentication, Machine Learning, Encryption}

Thousands of services are offered on \textit{web}, and the vast majority of these services use some form of authentication, usually through user and password. However, using passwords can make authentication fragile when it is very simple, with little security. On the other hand, when they are complex and very large they are difficult to memorize and users often keep notes of these in unsafe places, making the process fragile. In this way, password management systems can be a solution to avoid the use of weak and repeated passwords in different services without the need to be memorized by the user (or annotated). However, it is necessary to use efficient methods of authentication in these systems, because once someone can access them, all saved passwords can be seen. Thus, a good alternative is biometric authentication using features such as faces and voice, which can provide an extra layer of security while improving the convenience in its use. Machine learning techniques applied to biometric features have high recognition rates, and these results can be combined between different biometrics to improve security in the authentication process. The technology present in today's mobile devices allows the development of systems that are able to process biometric features with few computational resources, and have the necessary sensors for the process of collecting samples of them, through cameras, microphones and fingerprint reader. This work presents the project of a secure password management system using encryption and recognition of face and voice biometrics.
\end{abstract}



